Competing Bandits: \\ The Perils of Exploration under Competition

### 2018-11-06 paper/content/introduction.tex
tweaks to barriers intro

\gaedit{The findings on temporary monopoly shed light on the ``first-mover advantage" phenomenon in the digital economy. Being first in the market in the digital economy gives firms free data to learn from (a ``data advantage") as well as a more definite, and possibly better reputation compared to an entrant (a ``reputation advantage").

\swedit{Beyond the welfare implications, we also investigate the barrier to entry that follows from the incumbent's data advantage.  We run additional experiments that attempt to isolate the impact of the data advantage and reputation advantage. We find that the data advantage from the incumbent's ``small head start'' can lead to a significant incumbency advantage, especially when the incumbent commits to a more advanced bandit algorithm. Our results show that even a small degree of data asymmetry can be amplified to be a larger market advantage through competition dynamics. This is in contrast to the data advantage in a static environment such as discussed in \cite{varian2018artificial,bajari2018impact}, in which a small amount of additional data can only provide limited improvement in the predictive accuracy.
Our results shed lights on the importance of considering competition dynamics when reasoning about the anti-trust question of whether data can become a significant barrier to entry in an industry.
% in a competitive environment the relative differences in the data
% possessed by the firms may lead to a large competitive benefit due
% to the feedback loops discussed previously. In our model this effect
% is amplified when the incumbent commits to a more advanced bandit
% algorithm since, in the incumbency period, the firm gathers data on
% possible actions more efficiently leading to the relative gap upon
% entry to be larger. This is important when exploration can have
% larger reputational consequences.
}}\swcomment{still not super happy about above.}

>>>>

\gaedit{The findings on temporary monopoly shed light on the ``first-mover advantage" phenomenon in the digital economy. Being first in the market in the digital economy gives firms free data to learn from (a ``data advantage") as well as a more definite, and possibly better reputation compared to an entrant (a ``reputation advantage").}

\gaedit{Beyond the welfare implications, we also investigate the degree to which the incumbent's data advantage serves as a barrier to entry. We run additional experiments that attempt to isolate the impact of the data advantage and reputation advantage. We find that the data advantage from the incumbent's ``small head start'' can lead to a significant incumbency advantage, especially when the incumbent commits to a more advanced bandit algorithm. Our results show that even a small degree of data asymmetry can be amplified to be a larger market advantage through competition dynamics. This effect is more pronounced when the incumbent commits to a more advanced bandit algorithm since the incumbent does not have to suffer from the reputational consequences of exploration while the entrant does. Our results shed lights on the importance of considering competition dynamics when reasoning about the anti-trust question of whether data can become a significant barrier to entry in an industry.}
\gadelete{
\swedit{Beyond the welfare implications, we also investigate the barrier to entry that follows from the incumbent's data advantage.  We run additional experiments that attempt to isolate the impact of the data advantage and reputation advantage. We find that the data advantage from the incumbent's ``small head start'' can lead to a significant incumbency advantage, especially when the incumbent commits to a more advanced bandit algorithm. Our results show that even a small degree of data asymmetry can be amplified to be a larger market advantage through competition dynamics. \gadelete{This is in contrast to the data advantage in a static environment such as discussed in \cite{varian2018artificial,bajari2018impact}, in which a small amount of additional data can only provide limited improvement in the predictive accuracy.} The effect is stronger when the incumbent commits to a more advanced bandit algorithm due to

% in a competitive environment the relative differences in the data
% possessed by the firms may lead to a large competitive benefit due
% to the feedback loops discussed previously. In our model this effect
% is amplified when the incumbent commits to a more advanced bandit
% algorithm since, in the incumbency period, the firm gathers data on
% possible actions more efficiently leading to the relative gap upon
% entry to be larger. This is important when exploration can have
% larger reputational consequences.
}\swcomment{still not super happy about above.} }
